InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-31 paper.tex
Update midjourney part
Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>

Another image generative model is the \textbf{midjourney} \cite{midjourney}. This model was created by an independent research lab with the same name. It can synthesize images from textual descriptions. Midjourney tends to generate surrealistic images and is popular among artists and it uses modern deep learning methods to create high-quality images.

>>>>

Another image generative model is \textbf{midjourney} \cite{midjourney}. This model was created by an identically named and independent research lab. It can synthesize images from textual descriptions. Midjourney tends to generate surrealistic images and is popular among artists. It uses modern deep learning methods to create high-quality images.
